Appendix B

### 2021-11-06 manuscript.Rmd
* Packrat issue is solve Kniting will be continued for duplicate chunk names Font issue for plotting is solved

mainfont: Helvetica
appendix:
  - "instrument.Rmd"
  - "Appendix-B.Rmd"
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Helvetica")
```

```{r depMan, include=FALSE}
library(packrat)
packrat::init()

#To find and install required dependencies.
packrat::restore()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
install.packages("VIM")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
remotes::install_github("jthomasmock/gtExtras")
install.packages("questionr")
devtools::install_github("lbusett/insert_table")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
r_refs("references.bib")
```

@@

```{r CFA data frame, include=FALSE}

@@

```{r CFA 25items, include=FALSE }

@@

```{r CFA21}
LB.model.Cor.3 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1 
                       a1==a2
                       a3==a4

                       "

#item30 & 41 are removed

## Fit the model 
fit.Cor.3 <- cfa(LB.model.Cor.3, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")

rel.k.1 <- semTools::reliability(fit.Cor.3, return.total = T)
## Summary of Model 
cfa.sum.3 <- summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
                                  "cfi.scaled","tli.scaled",
                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))

@@

```{r cfa4F, eval=FALSE, include=FALSE}
LB.model.Cor.4 <- "F1 =~ a1*item16 + item36 + a2*item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 
                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                        a1==a2
                       a3==a4

                       "

## Fit the model 
fit.Cor.4 <- cfa(LB.model.Cor.4, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")

rel.k.4 <- semTools::reliability(fit.Cor.4, return.total = T)
## Summary of Model 
cfa.sum.4 <- summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
                                  "cfi.scaled","tli.scaled",
                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))

@@

```{r Invariance detail, include=FALSE}
# Configural invariance ####

@@

```{r IRT data, include=FALSE}
## Recoding sem.data$item8 into sem.data$Ritem8
sem.data$Ritem8 <- as.character(sem.data$item8)
sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
# Recoding sem.data$item26 
sem.data$Ritem26 <- as.character(sem.data$item26)
sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))

@@

>>>>

mainfont: Helvetica
appendix:
  - "instrument.Rmd"
  - "Appendix-B.Rmd"

---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Helvetica")
```

```{r depMan, include=FALSE}
library(packrat)
packrat::init(infer.dependencies = F)# install dependencies only for Rmd files in this project

#To find and install required dependencies.
packrat::restore()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("lavaan")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
install.packages("VIM")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")

install.packages("questionr")

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(extrafont)
extrafont::font_import()
r_refs("references.bib")
```

@@

```{r CFAdataframe, include=FALSE}

@@

```{r CFA25items, include=FALSE }

@@

@@

@@

```{r Invariancedetail, include=FALSE}
# Configural invariance ####

@@

```{r IRTdata, include=FALSE}
## Recoding sem.data$item8 into sem.data$Ritem8
sem.data$Ritem8 <- as.character(sem.data$item8)
sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
# Recoding sem.data$item26 
sem.data$Ritem26 <- as.character(sem.data$item26)
sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Appendix-B.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Appendix-B.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```
